---
title: "shiny-projects"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
#  install.packages("tidyverse")
library(tidyverse)
#  install.packages("jsonlite")
library(jsonlite)
# install.package("httr")
library(httr)
```

```{r init, include=FALSE}
source("toggl-helpers.R")
```

```{r clients, echo=FALSE}
clientsJSON <- getClients(togglToken, togglWid)

clients <- as.tibble(fromJSON(content(clientsJSON, "text")))
clients <- arrange(clients, name)
```

```{r users, echo=FALSE}
usersJSON <- getUsers(togglToken, togglWid)

users <- as.tibble(fromJSON(content(usersJSON, "text")))
users <- arrange(users, name)
```

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Projects

Two Shiny objects embedded below, the input dropdown is made up from the response when checking [toggl](www.toogl.com) for all clients in the workspace. Once you select the name of a client, a rest call will fetch the active projects for that client and present registered hours in a simple bar graph.


This depends on two environment variables: TOGGL_TOKEN and TOGGL_WORKSPACE


```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("client", label = "Client Name:", choices = c("", clients$name), selected = "NA"),
  selectInput("user", label = "User Name: ", choices = c("", users$name), selected = "NA")
)

renderPlot({
  if (input$client != "") {
    cId <- subset(clients, name == input$client)$id

    projectsJSON <- getProjects(togglToken, cId)
    projects <- as.tibble(fromJSON(content(projectsJSON, "text")))
    p1 <- projectPlot(projects, input$client)
    plot(p1)
  }
})
```
